### 2021-06-22 conclusionfutureworks.tex
implications + spell checker
additional pass on the conclusions sections

\section{conclusion and future work}

Mining sandboxes is a popular technique to isolate android applications to analyse their behavior and discover vulnerabilities. Currently most sandbox mining approaches use dynamic analysis and have been studied previously in detail by many including \blls. But the impact of static analysis on these mining approaches is unexplored currently. The use of static analysis techniques, like taint analysis algorithms, to detect malicious behaviours, seems promising and can leverage sandboxes accuracy. However, many authors argue in favor of dynamic analysis for  mining sandboxes, highlight limitations at static analysis at this task, neglecting the complement that could be obtained with it. To the best of our knowledge, this is the first work that explored the impact of static analysis at process of mining Android sandboxes for malware detect.

In this paper, we performed two studies. In the first we conducted a non-exact replication of \blls, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times. Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis. For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment. The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms. Enabling the Droidfax, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid). We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated. In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.

As future work, we plan to investigate other promising tools to enhance our data from previous executions. We will use the benchmark to test tools like Sapienz (a search-based test generation tool)~\cite{DBLP:conf/issta/MaoHJ16} and Dynodroid (an input generation system for Android apps) \cite{DBLP:conf/sigsoft/MachiryTN13}. And we will search for other great tools used by academia and by the industry to be tested by the benchmark DroidXP.
Also, we will execute each of the tools used in this experiment without the benchmark. And, we will compare these results with this experiment's results. This comparison will be valuable in the pursuit of one of this study's goals, which was to analyze what impact the benchmark droidXP has on its results.

>>>>

\section{Conclusions}

In this paper we reported the
results of two empirical studies that explore
techniques for Android malware identification.
The first study is a non-exact replication of a
previous research work~\cite{DBLP:conf/wcre/BaoLL18},
which investigates the Android mining sandbox
approach for malware identification. There,
Bao et al. report that more than 70\% of
the malwares in their dataset can be
detected by the sandboxes built from the
execution of five test case generation
tools (such as Monkey and DroidMate). Our replication
study revealed that this performance is only
achieved if we enable a static
analysis component from DroidFax that was supposed to only
instrument the Android \texttt{apk} files,
though that independently contributes to
building the sandboxes statically. As such,
the use of DroidFax leads to an
overestimation of the performance of the
mining sandbox approach supported by dynamic analysis.
Indeed, the execution of DroidFax alone enabled
us to generate a sandbox that can
identify 43.75\% of the malwares from 
their dataset.

In the second study we investigated
a new approach based on taint analysis
for malware identification, which
leads to promising results. First,
the taint based static analysis approach
detected 60.42\% of the
malwares in the dataset. When combining
taint analysis with the
mining sandbox approach, we were
able to identify 82.29\% of the
malwares in the dataset. These results
have implications for both researchers and
practitioners. First, we review the literature
showing, for the first time, empirical evidence
that the mining sandbox approach benefits
from using both dynamic and static analysis. Second,
practitioners can improve malware identification using
a combination of 
the mining sandbox approach with taint analysis.
Nonetheless, both the mining sandbox approach and
taint analysis present limitations. In particular,
we are not able to identify a malware that
uses the same set of calls to sensitive APIs of the
benign version of an app, using
the mining sandbox approach. Similarly, we are not
able to identify a malware that presents the same
paths from sources to sinks of the corresponding benign version of
an app, using the taint analysis approach. 
To mitigate these limitations, we envision the use of other approaches---such as machine learning
algorithms to classify changes in non-code assets (e.g., Android
manifest files) and symbolic execution to differentiate
malicious calls or source-sink paths.
